Monocle analysis of influenza-infected cells

### 2017-08-08 paper/key_refs.tex

@@

@@

@@

@@

\item \citet{kawakami2011strand} use qPCR to look at the accumulation of NP and NA in infected cells.
They suggest that NP mRNA reaches a peak around 6 hours of $5 \times 10^4$ / cell, whereas NA reaches a much lower peak and after more time.

>>>>

\item \citet{combe2015single} also look at the production of VSV from single infected cells, although immediately some of these cells are likely multiply infected. 
They find that the yield of viral progeny differs by about two orders of magnitude across cells.

\item \citet{heldt2015single} examine stochasticity during influenza virus infection.
They show that the amount of infectious progeny virions produced per infection (at high MOI) ranged from one to almost 1000.
They also show that the amount of vRNA per cell (again at high MOI infection) ranges by almost 3 orders of magnitude.
The amount of vRNA and progeny virions is strongly correlated.
For most segments, the amounts of different mRNAs is correlated.
They also have a bunch of simulations that I looked at less closely.

\item \citet{dou2017analysis} use an RNA-labeling method to look at the presence of vRNAs in single infected cells.
By their method, they find that only about 20\% of cells contain all 8 vRNPs.
They also show that there is a very limited window for co-infection.

@@

\item \citet{davis1980influenza} is an old paper that appears to be the original one showing that influenza defective RNAs have both termini and so represent some type of internal deletion.

\item \citet{odagiri1997segment} look at a PA defective segment in the presence of an NS2 mutant.
They show that the shorter defective PA segment is favored at both the levels of segment replication and genome packaging. 
I remain a bit unclear about how the NS2 mutant plays into all of this, other than that apparently this NS2 mutant generates lots of PA defectives...

\item \citet{hutchinson2008mutational} look at how many infected cells lack expression of at least one of two segments tested.
They find that for wildtype virus this is about 20\%, but when there are synonymous mutations in the packaging signal of M, then it is about 50\%.

@@

\item \citet{brooke2013most} show that over half of cells infected with PR8 fail to express one of four proteins tested.
High MOI infection alleviates this incomplete expression, presumably via co-infection with viruses each of which fails to express different genes.

\item \citet{brooke2014influenza} find a mutation in NP that specifically reduces the packaging of NA in a way that is advantageous in guinea pigs.
They do various things showing that co-infection occurs \textit{in vivo}, and also show that there is at least some amount of dose-response in terms of gene expression as cells that get lots of no-NA virus during co-infection express relatively less NA protein.

@@

\item \citet{perez2014unbiased} looks at type I IFN induction in A549 cells with a fluorescent reporter.
The wildtype virus induces IFN in a few percent of cells.
A NS1-deletion virus induces in 15-20\% of cells.
They passage in IFN-deficient cells to isolate various mutants that induce more than wildtype but less than the delta-NS1 virus.
Most of these mutations are in proteins other than NS1, including some in M1 that were shown to induce IFN more effectively.
They also argue that some of the inducing mutations lead to more defective segments to accumulate.

\item \citet{killip2015influenza} reviews IFN induction by influenza, including the point that only a fraction of cells induce IFN upon infection.

\item \citet{killip2017single} look at IFN induction by wildtype and NS1-defective influenza virus.
Although some viruses (like Sendai) are able to induce IFN expression in almost all their cells, influenza only induces IFN in less than one percent of cells.
An NS1-defective virus induced IFN in many more cells, but it was still only 5 to 20\%.
In neither case is there an obvious correlation between NP protein production and IFN activation -- IFN is both present and absent in cells with little and lots of NP.

@@

\citet{vreede2004model} This paper examines production of mRNA and cRNA in the presence of cycloheximide.
They demonstrate the cRNA production requires the presence of the polymerase proteins (PB2, PB1, PA, NP) in excess of those in the initial vRNAs, although the PB1 can be inactive.

\item \citet{kawakami2011strand} use qPCR to look at the accumulation of NP and NA in infected cells.
They suggest that NP mRNA reaches a peak around 6 hours of $5 \times 10^4$ / cell, whereas NA reaches a much lower peak and after more time.
The paper also shows that mRNA levels peak at 4-6 hours regardless of the presence or absence of cycloheximide, but the mRNA production is less in the presence of cycloheximide indicating secondary transcription.
